---
title: "Lab1"
author: "He Jiang; Matt Stuart"
date: "January 19, 2017"
output: html_document
---

## Build A Book 

We had code running to create a pdf from XeLaTex, but get stuck using this code: 
system("makeindex advanced-r")
Couldn't find input index file advanced-r nor advanced-r.idx.
Usage: makeindex [-ilqrcgLT] [-s sty] [-o ind] [-t log] [-p num] [idx0 idx1 ...]
Warning message:
running command 'makeindex advanced-r' had status 1 

We seem to not receive an index file to run the code.  How should we go about obtaining this index file?
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Weather Stations

This a function to input a station, and return the plot your expect.
```{r}
library(tidyverse)

tmax <- function(stationid){
  if (nchar(stationid) != 6) {leadzero <- paste(c(rep(0,each=6-nchar(stationid))),collapse='')} else {leadzero <- ""}
  name <- paste("USH0",leadzero,stationid,".raw.tmax",sep="")
temps <- read_fwf(name,
                  col_positions = fwf_positions(
                    start=c( 1,13, rep(16+9*0:11, each=4) + c(1,7,8,9)), 
                    end  =c(11,16, rep(16+9*0:11, each=4) + c(6,7,8,9))))
names(temps) <- c("Station", "Year", 
                  paste0(rep(c("Value","DMflag", "QCflag", "DSflag"), 12), 
                         rep(1:12, each=4)))

stationid <- temps %>% 
  gather(key="Month", value="Temp_Max", starts_with("Value"))
stationid$Month <- as.numeric(gsub("Value", "", stationid$Month))
stationid$Temp_Max <- replace(stationid$Temp_Max, 
                              stationid$Temp_Max == -9999, NA)

return(stationid %>% ggplot(aes(x = Year, Temp_Max/100)) + 
  geom_point() + facet_wrap(~Month, nrow=2))
}
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
